Exploring and understanding the Interdependence of Collaboration Networks

### 2018-08-22 draft.tex
edit2 draft files

@@

\subsubsection{Probability that pairs Co-author given they exchange non-zero citation in the past:}
We define $P(C)$ as probability that they cite each other before collaborating in  $t$ and $P_{n}(c)$ as probability that the pair have cited each $n$ years before collaboration in $t$. 
There fore we have:
\begin{equation}
P(C) = P_{1}(c) + P_{2}(c) + \dots + P_{t-T_0}(c) 
\end{equation}
$T_0$ is time of first co appearance. Let $P(D=1)$ be probability of co-authoring then we have:
\begin{equation}
P(D=1|C) = \frac{P(C|D=1).P(D=1)}{P(C)}
\end{equation}

@@

\captionsetup{singlelinecheck=false, justification=raggedright,  labelsep=space}
\caption{Total number of citations between pairs of authors VS distance D between pairs in the co-authorship network(for all years till 2013)}
   \label{f4}
\end{figure}

>>>>

\begin{figure}
	\centering
	\includegraphics[scale = 0.45]{plots/cit_dnot1}

	\captionsetup{singlelinecheck=false, justification=raggedright,  labelsep=space}
	\caption{Number of author pairs that co-author but do not cite each other.}
	\label{ftwo}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[scale = 0.45]{plots/rec}

	\captionsetup{singlelinecheck=false, justification=raggedright,  labelsep=space}
	\caption{Number of author pairs that co-author but do not cite each other.}
	\label{freci}
\end{figure}
\subsubsection{Probability that pairs Co-author given they exchange non-zero citation in the past:}
We define $P(C)$ as probability that they cite each other before collaborating in  $t$ and $P_{n}(c)$ as probability that the pair have cited each $n$ years before collaboration in $t$. 
There fore we have:
\begin{equation}
P(C) = P_{1}(c) + P_{2}(c) + \dots + P_{t-T_0}(c) 
\end{equation}
$T_0$ is time of first co appearance. Let $P(D=1)$ be probability of co-authoring then we have:
\begin{equation}
P(D=1|C) = \frac{P(C|D=1).P(D=1)}{P(C)}
\end{equation}

@@

\captionsetup{singlelinecheck=false, justification=raggedright,  labelsep=space}
\caption{Average Total number of citations between pairs of authors VS distance D between pairs in the co-authorship network(for years till 1990,2000 and 2013)}
   \label{f4}
\end{figure}
